Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

Recall that triplet-based model is already prone to collapse with very hard
examples, even if they are unperturbed.
%
Similarly, the model is expected to collapse with excessively hard adversarial
examples as well.
%
As shown in the last three columns of \cref{tab:desth}, almost all combinations
will result in model collapse as long as the destination hardness is softhard,
distance, or hardest.
%
The only exception is the combination of distance and hardest.
%
We speculate the  \oo{TODO}
The $E[H]$ of distance and hardest sampling are empirically observed very close.
%

And the model can be easier to collapse with adversarially perturbed hard
examples

>>>>

Recall that triplet-based model is already prone to collapse with very hard
examples, even if they are unperturbed.
%
Similarly, the model is expected to collapse with excessively hard adversarial
examples as well.
%
As shown in the last three columns of \cref{tab:desth}, almost all combinations
will result in model collapse as long as the destination hardness is softhard,
distance, or hardest.
%
The only exception is the combination of distance and hardest.
%
We empirically observe that the $E[H]$ of distance and hardest sampling are
very close to each other, which means the attack will be rather weak.
%
The model does not collapse in this case, but the robustness gain is negligible
as well.
